\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-25 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Section V

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We next consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{align}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

>>>>

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We next consider a power network with $n=20$ generators, and propagate the transient joint state PDFs supported over the 40 dimensional state space $\mathbb{T}^{20}\times\mathbb{R}^{20}$. We take the initial joint state PDF at $t=0$ as
\begin{align}
\rho_{0}\equiv\rho(t=0,\theta(0),\omega(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{align}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.
